RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2022-12-08 main.tex
:pencil: Update literature review

\begin{document}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From State Distribution}
% \title{RIScatter: Bridging Backscatter Modulation and Passive Beamforming With Adaptive State Distribution}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
		B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
	}
}
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal characteristics (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% x Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% ? semicoherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence, base 2 in simulation
% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% * SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% ? Channel estimation error, coordination issues

@@

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of the active primary and passive backscatter links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	% Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
\end{abstract}

@@

		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig. \subref*{fg:mbc} and \gls{bbc} in Fig. \subref*{fg:bbc}.

@@

		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but backscatter decoding is subject to the strong interference from the primary (legacy) link.
		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, where the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
		This concept was further refined by \cite{Liang2020} as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.

@@

		On the other hand, \gls{ris} in Fig. \ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and optimized based on \gls{csi}.

@@

		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
		A comparison of those scattering applications is summarized in Table \ref{tb:scattering_applications}.

@@

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                                        & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
			\showrowcolors
			Coexisting link(s)                                      & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
			Primary/Backscatter modulation                          & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
			Primary impact on backscatter detection                 & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
			Backscatter impact on primary detection                 & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
			Cooperation devices                                     & ---                 & No                 & Co-located receiver (and primary transmitter) & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
			Cooperative decoding strategy                           & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
			Primary detection                                       & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
			Backscatter detection                                   & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
			Reflection pattern over time depends on                 & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
			Reflection state (i.e., backscatter input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
			Load-switching speed                                    & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
		Joint \gls{ml} decoding provides the best error performance for \gls{sr} but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
		One special property of those active-passive coexisting networks is that the backscatter signal strength can be relatively weak due to the double fading effect.
		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
		Another open issue for \gls{bc} is the efficient backscatter multiple access design.
		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy during others.
		It enables adaptive transmission time and reflection ratio optimization but incurs high coordination cost.
		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher node power consumption.
		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
		This code-domain solution suffers from the near-far problem and imperfect synchronization, both can be very severe in low-power backscatter scenarios.

		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
		On the other hand, dynamic \gls{ris} with independent reflection patterns at different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode message at the \gls{ris}.
		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite input constellations.
		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and multiplication coding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can indeed outperform passive beamforming at high \gls{snr}.
		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
		In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
		However, those joint designs incur advanced hardware architecture and high optimization complexity.
		Relevant \gls{bc} literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit \gls{csi} and signal characteristics.
		For active-passive coexisting networks, it has been observed that:
		1) \gls{rf} waves on the air can be effectively recycled by smart scattering;
		% 2) transmitter-scatter-receiver paths can be used to simultaneously control wireless channels and establish passive connections;
		2) transmitter-scatter-receiver paths can be exploited simultaneously for backscatter modulation and passive beamforming;
		3) co-located primary and backscatter receiver enables interference cancellation and cooperative decoding;
		4) the primary and backscatter symbols are superimposed by multiplication (i.e., double modulation).
	\end{subsection}

	\begin{subsection}{Contributions}
		% The concept of RIScatter is illustrated in Fig. \subref*{fg:riscatter} and the contributions of this paper are summarized below.
		% As presented in Fig. \subref*{fg:riscatter}, we envision RIScatter as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
		% We envision RIScatter in Fig. \subref*{fg:riscatter} as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
		% The contributions of this paper are summarized below.

@@

		% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
		% As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
		% partially engineer the wireless channel and partially modulate its own information.
		% This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
		% As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
		% This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.

>>>>

\begin{document}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From State Distribution}
% \title{RIScatter: Bridging Backscatter Modulation and Passive Beamforming With Adaptive State Distribution}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
		B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
	}
}
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal characteristics (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% x Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% ? semi-coherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence, base 2 in simulation
% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% * SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% ? Channel estimation error, coordination issues

@@

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	RIScatter consists of multiple dispersed or co-located scatter nodes, whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of the coexisting active primary and passive backscatter links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	% Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks without \gls{sic}.
\end{abstract}

@@

		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.

@@

		As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
		This concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually or sequentially decodes both links.

@@

		On the other hand, \gls{ris} in Fig.~\ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and optimized based on \gls{csi}.

@@

		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, which may also be exploited at the primary transmitter for cooperative active beamforming.
		A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.

@@

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.4}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                                 & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
			\showrowcolors
			Coexisting link(s)                               & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
			Primary/Backscatter modulation                   & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
			Primary impact on backscatter detection          & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
			Backscatter impact on primary detection          & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
			Cooperative devices                              & ---                 & No                 & Primary transmitter and co-located receiver   & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
			Cooperative decoding strategy                    & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
			Primary detection                                & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
			Backscatter detection                            & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
			Reflection pattern over time depends on          & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
			Reflection state (i.e., node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
			Load-switching speed                             & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Arbitrary                                                               \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, active-passive coexisting networks can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
		Joint \gls{ml} decoding provides the best error performance but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
		Indeed, active-passive coexisting networks have three special and important properties:
		% 1) there exists a \emph{double modulation} where primary and backscatter symbols are superimposed by multiplication coding;
		1) primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		2) backscatter \emph{signal strength} is much weaker than primary because of the double fading effect;
		3) backscatter \emph{symbol period} is longer than primary because of the load switching constraint.
		% ! double modulation, double fading, symbol period difference
		The last two motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
		% During primary decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the backscatter-over-primary symbol period ratio $N$\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
		During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty (resp. multiplicative interference) when the backscatter-over-primary symbol period ratio $N$ is large (resp. small)\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
		% , depending on the backscatter-over-primary symbol period ratio $N$\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
		Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive, since it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
		On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
		It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
		This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher node power consumption.
		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
		This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in low-power backscatter scenarios.

		Conventional \gls{ris} design with fixed reflection coefficients during each channel block has been extensively studied in communication, sensing, and power literatures \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
		On the other hand, dynamic \gls{ris} with independent reflection patterns in different time slots has gained recent attentions in multi-user and multi-purpose wireless networks.
		The concept was first proposed in \cite{Yang2020} to fine-tune the \gls{ofdm} resource blocks, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
		It introduces artificial channel diversity and enables flexible resource allocation, but misses the opportunity to encode its own message.
		\gls{ris} can also be used as a transmitter when placed in the near field of a carrier emitter, and prototypes for \gls{psk} and \gls{qam} have been implemented in \cite{Tang2019a,Dai2020a}.
		From an information-theoretic perspective, \cite{Karasik2020} reported that using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal for finite input constellations.
		Instead, the capacity of \gls{ris}-aided channel is achieved by joint transmitter-\gls{ris} encoding, and \gls{sic}-based \gls{sr} can outperform passive beamforming at high \gls{snr}.
		It inspired \gls{ris}-empowered \gls{bc} \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall reflection pattern.
		In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
		However, those joint designs incur advanced hardware architecture and high optimization complexity.
		Relevant literatures also consider either \emph{Gaussian} codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite \emph{equiprobable} inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit \gls{csi} and signal properties.
		% For active-passive coexisting networks, it has been observed that:
		% 1) the transmitter-scatter-receiver path can be exploited to adjust wireless channel and establish passive connection;
		% 2) co-located receiver enables interference cancellation and cooperative decoding;
		% 3) the primary and backscatter symbols are superimposed by multiplication (i.e., double modulation).
	\end{subsection}

	\begin{subsection}{Contributions}
		% The concept of RIScatter is illustrated in Fig.~\subref*{fg:riscatter} and the contributions of this paper are summarized below.
		% As presented in Fig.~\subref*{fg:riscatter}, we envision RIScatter as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
		% We envision RIScatter in Fig.~\subref*{fg:riscatter} as a novel scatter protocol that generalizes \gls{bc} and \gls{ris}.
		% The contributions of this paper are summarized below.

@@

		% \emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
		% As shown in Fig.~\subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
		% partially engineer the wireless channel and partially modulate its own information.
		% This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
		% As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
		% This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
